Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-26 paper.tex
Answered a note

% Summary of contributions
We reviewed architectures used to integrate workflow engines in
science gateways, we described them in a system-independent framework
suitable for comparison, we illustrated them on real systems, we
developed quantitative metrics for evaluation, we evaluated these
metrics for all the architectures, and we discussed the pros and cons
of all the architectures based on these metrics.  \note{Rafael}{One
  thing that is missing in the conclusion or the limitations section
  is to state that this work does not intend to quantify the amount of
  work required to develop science gateways using a specific
  architecture, but the goal is to highlight what are the main
  components and interactions for each architecture, and the main
  advantages and drawbacks. This should also be stated in the
  introduction.}

>>>>

% Summary of contributions
We reviewed architectures used to integrate workflow engines in
science gateways, we described them in a system-independent framework
suitable for comparison, we illustrated them on real systems, we
developed quantitative metrics for evaluation, we evaluated these
metrics for all the architectures, and we discussed the pros and cons
of all the architectures based on these metrics.  \answerednote{Rafael}{One
  thing that is missing in the conclusion or the limitations section
  is to state that this work does not intend to quantify the amount of
  work required to develop science gateways using a specific
  architecture, but the goal is to highlight what are the main
  components and interactions for each architecture, and the main
  advantages and drawbacks. This should also be stated in the
  introduction.}{Tristan}{This is in contradiction with the metric on
  'integration effort'. What do you think?}
